Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-06-16 extended_catalog/paper/extended_catalog.tex
Improved bibliography

\usepackage{rotating}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xspace}

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Fermi Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that were done to validate this tool.
We then calculate the Fermi LAT's sensitivity to spatially exnteded
sources.
We then apply this tool to test all sources in the 2FGL Two Year Catalog
for extension.\cite{2FGL} We then report on the discovery of XXXXXXXXXXXXXX new
extended sources.
\end{abstract}

@@

In particular, the LAT has discovered a variety of spatially extended
supernova remnants including IC443 and W51C (\cite{IC443,W51C}) and pulsar
wind nebulae (\cite{MSH15-52,VelaX}). And there are other source classes
which could possibly be spatially resolved by the LAT including galaxy
clusters, dark matter, and possibly new physics.

@@

In principle, the entire task can be done using the standard science
tools package \gtlike\cite{Science-Tools-gtlike}. But \gtlike is
only able to fit the spectral parameters of the source, so the extension
fitting would have to be done as an external loop. Typically, the run time
for a binned source analysis using \gtlike is several hours so this loop
would be especially time consuming. In principle, parallel computing could
ease this burdon, but parallel fitting algorithms are rather untested
and complex. Furthermore, the machinery required to do something like
this would necessarily be rather complex. What has typically been done by
the Fermi team to study extended sources is to fix the assumed position
of the extended source, either by our knowledge of a source from other
wavelenghts, or by fitting it as a point source. Then, a profile of the
likelihood as a function of extension is developed using \gtlike
and the maximum of this profile. This approach is not optimal because it
needs not be the case that the best fit position of a point source would
be the same as the best fit position of an extended source. Furthermore,
by not fully maximizing the likelihood, this method is not as significant to
extension, especially of faint sources. And finally, since this approach
is so computationally intensive, no large scale Monte Carlo effort has been
launched to validate the method.

Instead, an alternate approach was developed for performing
a morphological analysis. An alternate maximum likelihood fitting
package called \pointlike has been developed by the Fermi
collaboration and we have expanded its functionality to fully support
analyzing spatially extended sources. \pointlike is most thoroughly
described in Matthew Kerr's Ph.D Thesis\cite{matthew_kerr_phd_thesis}
but the important aspects will be summarized below. What differentiates
\pointlike most significantly from \gtlike is its emphasis
on speed by introducing approximations into the calculation of the
likelihood function while at the same time trying to reduce any
numerical errors that may be introduced.  Like binned \gtlike,
\pointlike bins the sky both in position and energy.  Unlike 
\gtlike, \pointlike relies on the {\em healpix} representation of spatial
bins\cite{healpix_paper} and scales the size of each spatial bin to be
smaller than the PSF. This is convenient because it no
significant information is lost due to binning at all energies and it is
always a good approximation that the model predicted counts are uniform
across a spatial bin.

@@

Errors on fit parameters are typically calculated in one of two ways. The
first method requires explicilty varying one paramter until the log of
the likelihood has fallen by a value 1/2 while simulatenously optimizing
the other fit parmaeters.  \minuit provides the {\em Simplex} function to
calculate errors this way.\cite{minuit documentation and UP parameter}
The second method involves estimating the likelihood function as being
a multivariate gaussian and calcluating the curvature of the log of
the likelihood at the peak to estimate when the function will fall by
a value 1/2. \minuit provides the {\em HESSE} algorithm to calcualte
errors this way.  The {\em HESSE} are significantly faster but make the
approximation that the log of the likelihood is perfectly gaussian.

@@

Then, the extended source's position error is calculated using the
same code employed to calculate position errors of point sources. This
code is used to calculate the localization error of all point sources
in the catalog\cite{2FGL paper}. It works by fitting an ellipse to the
likelihood surface near the maximum and using this fit ellipse to estimate
an elliptical localization errors. By reporting two localization errors
as well as a localization error angle, this method explicitly takes care
of covariance between the two position coordinates.

@@

The half $\chi^2_1$ distribution was found by a monte carlo study
to hold for the special case of source finding of EGRET sources using the
maximum likelihood technique.  They were comparing the hypothesis of a
source to the hypothesis of just a background\cite{Mattox_et_All_Paper}.
Their argument for why this null hypothesis distribution was reasonable
was that half of the time, statistical underfluctuations would cause
there to be fewer fewer photons then expected where the sources is being
tested. Since the maximim likelihood machinery cannot fit negative
sources (which would lead to negative model predicted for which the
poisson likelihood is undefined), half of the tests would not have the
likelihood improved by adding a source to the model and $\ts=0$.
It is for the case that the null distribution has

@@

Fermi LAT data was simulated using the publically avaliabable Science
Tools package \gtobssim\cite{GTOBSSIM_CITATION}. The sources were
simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
fluxes ranging from $3\times 10^{-9} \ph/\cm^2/s$ to 
$10^{-6} \ph/\cm^2/s$.
The sources were then simulated with spectral index ($\gamma$) values of
1.5, 2, 2.5, and 3.  These values were picked to probe a representative
range measurable values.  For particular spectral indices, only the
fluxes which would create a statistically significant source detection
($\ts>25$) where selected, since we are only interested in
testing for extension sources with a significant extent. The sources were
simulated on top of an isotropic powerlaw background with a Sreekumar-like
spectrum ($>100\mev$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
et al. ApJ 494 pag 523 1998}

@@

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a uniform radially symmetric
disk morphology on top of a powerlaw Sreekumar-like isotropic
spectrum.\cite{Sreekumar et al. ApJ 494 pag 523 1998}.  The monte carlo
simulation was perforormed over a one year time interval using a default
rocking profile and an assumed a represntative livetime fraction of 0.8.
For a given extension and spectral index, we calculated the
sensitivity by varying the flux of a source until we found 
when $\tsext=25$. In particular, we hand picked a flux range
where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
a log uniform distribution in this range and performed an extension
test for each of these fluxes. Since the measured signifciance is
a statistical which will vary from realization to realization,
we then repeated this procedure $>15$ times for each spectral
and spatial model.
By fitting a line to the flux vs $\tsext$ data, we were able to
estimage the flux at which $\tsext=25$.

@@

The LAT two year catalog presented a search for all
statistically significant sources that are detected in the $\gev$
sky\cite{2FGL_catalog}.  The catalog group's source finding method assumes
that the emission originated as point sources and what was presented was
a list of all sources fit assuming a point source spatial hypothesis. 
Published extended sources were modeled by the catalog group as 
being extended, but no attempt was made to test if other sources in the catalog
could be spatially resolved.

@@

We also performed a search for extended sources using events only between
10\gev and 100\gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and is
likely not perfectly modeled. On the other hand, at the highest energies
accessible by the LAT, the galactic diffuse emission will be smaller and
we might expect to detect significantly harder sources. This approach is
also beneficial because harder sources with nearby neighbors that are
softer may end up being incorrectly fit at lower energies but correctly
found looking only at the high energy.  This is also beneficial in the
galactic plane looking for possible extended sources near pulsars which
are very bright at lower energy but cutoff before 10\gev.  This approach
of using only events above $10\gev$ was succesfully used to detecting
HESS J1825-137 with the Fermi LAT~\cite{HESS J1825 paper}.

@@

We expect most extended sources to be galactic sources since extragalactic
sources are typically too far away to be resolvable. Unfortunately,
the \gev emission in the galactic plane is dominated by anisotropic
galactic diffuse emission.  Modeling the galactic diffuse emission is
very difficult~\ref{first_diffuse_paper}  and finding sources on top of
this emission is notoriously difficult. This issue has been discussed
in the Fermi catalog~\ref{1FGL,2FGL}. Furthermore, the galactic plane
is very crowded and there is a degeneracy between an extended source
and multiple point sources. So it is often difficult to ensure you have
a good model for the region around a source .  Finding a source with
$\tsext>16$ is not sufficient for detecting an extended and we had to
perform many crosschecks to make sure we had a good fit to our region.

@@

% XXXXXXXXXXXXXXXXXXXXXXXXXXX
% Put example of poorly fit region and how it is difficult to know what
% is going on.

@@

Using events above $10\gev$, we were able to succesffuly fit the extesion
of HESS J1825-137\cite{HESS 1825 paper}. Our analysis of MSH 15-52 using
events above $10\gev$ found an extension consistent with the publisehed
result, but with $\tsext=11.2$.\cite{MSH 15-52 Paper}. This
is most likely because the published analysis used events above $6\gev$.

@@

AGN are not expected to be spatially resolvable and therefore
provide a good calibration source to demonstrate the efficacy of our
tool. Nevertheless, it would be very interesting if AGN could be
spatially resolved AGN and there are theories that predict
this\cite{pair_halo_paper, http://adsabs.harvard.edu/doi/10.1086/187222}.

Following the Fermi-LAT one year catalog, the Fermi collaboration
published a list of the Fermi catalog sources that had a high probability
association with AGN. The first year catalog had 709 AGN associated with
671 distinct 1FGL sources at high latitude ($|b|>10\deg$).  For our
study, we are looking to assess systematics with extension fitting so
it is important to avoid any possible issues with AGN associations.
For that reason, we select only the 599 AGN which make it into the
``clean'' AGN sample. An AGN association is only considered ``clean''
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the 1FGL source, and if there are no flags
on the source which shed doubt on the source\cite{1FGL}. These last two
conditions are especially important for our analysis. One might expect
source confusion between two AGN look like a spatially extended source.
Testing only unflagged sources is also important because it removes
any catalog sources coincident with structures in the diffuse emission.
It is possible that these flagged catalog sources which are really poorly
modeled diffuse emission might also look extended.

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{This is the Fermi LAT's sensitivity to spatially
    extended sources. The $x$ axis is Monte Carlo extension of a
    simulated uniform disk source and the $y$ axis is the simulated
    source's $100\mev$ to $100\gev$ photon flux. Each curve represents
    the detection threshold for being able to spatially resolve an
    extended source (when $\langle\tsext\rangle=25$ averaged over
    multiple simulations).  
    All sources have an assumed powerlaw spectrum and the different
    colors are for sources of different simulated spectral indices.
    The dashed line shows simulations using events with energy between 
    $100\mev$ and $100\gev$ while the solid lien shows simulations
    using events with energy between $1\gev$ and $100\gev$.
    The sensitivity is for a one year simulation against a Sreekumar-like
    isotropic background\cite{Sreekumar et al. ApJ 494 pag 523 1998}.
    This plot shows that our sensitivity is best for sources that are
    about $1\deg$ large. It also shows that for sources That are neither
    very large nor very soft, our sensitivity is not significantly
    improved using events between $100\mev$ and $1\gev$.  More information
    about this plot is presented in section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

% XXXXXXXXXXXXXXXXXXXXXXX
% example bad fit
% P72Y3047

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
  \caption{1FGL J1628.6-2419c. In the opiucus region=most likeliy a molecular cloud.
  P72Y2516.
  Note that unlike other plots, that this plot has the nearby sources subtracted.
  This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
  which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
  }\label{1FGL_J1628.6-2419c}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
  \caption{1FGL J0823.3-4248. P72Y1212. Coincident with Puppis A SNR.
  P72Y1212.
  Note that unlike most other plots, this plot has the nearby sources subtracted.
  This was done to remove the very bright source Vela which,
  at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
  would otherwise spill over into the top left of the image.
  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
  }\label{1FGL_J0823.3-4248}
\end{figure}

>>>>

\usepackage{rotating}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{url}

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Fermi Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that were done to validate this tool.
We then calculate the Fermi LAT's sensitivity to spatially exnteded
sources.  We then apply this tool to test all sources in the 2FGL Two
Year Catalog for extension.\cite{2fgl} We then report on the discovery
of XXXXXXXXXXXXXX new extended sources.
\end{abstract}

@@

In particular, the LAT has discovered a variety of spatially extended
supernova remnants including IC443 and W51C (\cite{ic443,w51c}) and pulsar
wind nebulae (\cite{msh1552,velax}). And there are other source classes
which could possibly be spatially resolved by the LAT including galaxy
clusters, dark matter, and possibly new physics.

@@

In principle, the entire task can be done using the 
official maximum likelihood tool \gtlike which is 
distributed publically by the Fermi Science Support Center\cite{fssc}. 
But \gtlike is
only able to fit the spectral parameters of the source, so the extension
fitting would have to be done as an external loop. Typically, the run time
for a binned source analysis using \gtlike is several hours so this loop
would be especially time consuming. In principle, parallel computing could
ease this burdon, but parallel fitting algorithms are rather untested
and complex. Furthermore, the machinery required to do something like
this would necessarily be rather complex. What has typically been done by
the Fermi team to study extended sources is to fix the assumed position
of the extended source, either by our knowledge of a source from other
wavelenghts, or by fitting it as a point source. Then, a profile of the
likelihood as a function of extension is developed using \gtlike
and the maximum of this profile. This approach is not optimal because it
needs not be the case that the best fit position of a point source would
be the same as the best fit position of an extended source. Furthermore,
by not fully maximizing the likelihood, this method is not as significant to
extension, especially of faint sources. And finally, since this approach
is so computationally intensive, no large scale Monte Carlo effort has been
launched to validate the method.

Instead, an alternate approach was developed for performing
a morphological analysis. An alternate maximum likelihood fitting
package called \pointlike has been developed by the Fermi
collaboration and we have expanded its functionality to fully support
analyzing spatially extended sources. \pointlike is most thoroughly
described in Matthew Kerr's Ph.D Thesis but the important aspects will
be summarized below (\cite{matthew_kerr_thesis}) . What differentiates
\pointlike most significantly from \gtlike is its emphasis
on speed by introducing approximations into the calculation of the
likelihood function while at the same time trying to reduce any
numerical errors that may be introduced.  Like binned \gtlike,
\pointlike bins the sky both in position and energy.  Unlike 
\gtlike, \pointlike relies on the {\em healpix} representation of spatial
bins\cite{healpix} and scales the size of each spatial bin to be
smaller than the PSF. This is convenient because it no
significant information is lost due to binning at all energies and it is
always a good approximation that the model predicted counts are uniform
across a spatial bin.

@@

Errors on fit parameters are typically calculated in one of two ways. The
first method requires explicilty varying one paramter until the log of
the likelihood has fallen by a value 1/2 while simulatenously optimizing
the other fit parmaeters.  \minuit provides the {\em Simplex} function to
calculate errors this way (\cite{minuit_documentation}).
The second method involves estimating the likelihood function as being
a multivariate gaussian and calcluating the curvature of the log of
the likelihood at the peak to estimate when the function will fall by
a value 1/2. \minuit provides the {\em HESSE} algorithm to calcualte
errors this way.  The {\em HESSE} are significantly faster but make the
approximation that the log of the likelihood is perfectly gaussian.

@@

Then, the extended source's position error is calculated using the
same code employed to calculate position errors of point sources. This
code is used to calculate the localization error of all point sources
kn the catalog\cite{2fgl}. It works by fitting an ellipse to the
likelihood surface near the maximum and using this fit ellipse to estimate
an elliptical localization errors. By reporting two localization errors
as well as a localization error angle, this method explicitly takes care
of covariance between the two position coordinates.

@@

The half $\chi^2_1$ distribution was found by a monte carlo study
to hold for the special case of source finding of EGRET sources using the
maximum likelihood technique.  They were comparing the hypothesis of a
source to the hypothesis of just a background\cite{mattox_egret}.
Their argument for why this null hypothesis distribution was reasonable
was that half of the time, statistical underfluctuations would cause
there to be fewer fewer photons then expected where the sources is being
tested. Since the maximim likelihood machinery cannot fit negative
sources (which would lead to negative model predicted for which the
poisson likelihood is undefined), half of the tests would not have the
likelihood improved by adding a source to the model and $\ts=0$.
It is for the case that the null distribution has

@@

Fermi LAT data was simulated using program \gtobssim which is
distributed publically by the Fermi Science Support Center
(\cite{fssc}).  The sources were simulated with a powerlaw spectral
model with 6 Were given 6 $>100\mev$ fluxes ranging from $3\times 10^{-9}
\ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.  The sources were then simulated
with spectral index ($\gamma$) values of 1.5, 2, 2.5, and 3.  These
values were picked to probe a representative range measurable values.
For particular spectral indices, only the fluxes which would create a
statistically significant source detection ($\ts>25$) where selected,
since we are only interested in testing for extension sources with a
significant extent. The sources were simulated on top of an isotropic
powerlaw background with a Sreekumar-like spectrum ($>100\mev$ flux
of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).

@@

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a uniform radially symmetric
disk morphology on top of a powerlaw Sreekumar-like isotropic
spectrum (\cite{sreekumar_isotropic}).  The monte carlo
simulation was perforormed over a one year time interval using a default
rocking profile and an assumed a represntative livetime fraction of 0.8.
For a given extension and spectral index, we calculated the
sensitivity by varying the flux of a source until we found 
when $\tsext=25$. In particular, we hand picked a flux range
where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
a log uniform distribution in this range and performed an extension
test for each of these fluxes. Since the measured signifciance is
a statistical which will vary from realization to realization,
we then repeated this procedure $>15$ times for each spectral
and spatial model.
By fitting a line to the flux vs $\tsext$ data, we were able to
estimage the flux at which $\tsext=25$.

@@

The LAT two year catalog presented a search for all
statistically significant sources that are detected in the $\gev$
sky\cite{2fgl}.  The catalog group's source finding method assumes
that the emission originated as point sources and what was presented was
a list of all sources fit assuming a point source spatial hypothesis. 
Published extended sources were modeled by the catalog group as 
being extended, but no attempt was made to test if other sources in the catalog
could be spatially resolved.

@@

We also performed a search for extended sources using events only between
10\gev and 100\gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and is
likely not perfectly modeled. On the other hand, at the highest energies
accessible by the LAT, the galactic diffuse emission will be smaller and
we might expect to detect significantly harder sources. This approach is
also beneficial because harder sources with nearby neighbors that are
softer may end up being incorrectly fit at lower energies but correctly
found looking only at the high energy.  This is also beneficial in the
galactic plane looking for possible extended sources near pulsars which
are very bright at lower energy but cutoff before 10\gev.  This approach
of using only events above $10\gev$ was succesfully used to detecting
HESS J1825-137 with the Fermi LAT~\cite{fermi_hess_j1825}.

@@

We expect most extended sources to be galactic sources since extragalactic
sources are typically too far away to be resolvable. Unfortunately,
the \gev emission in the galactic plane is dominated by anisotropic
galactic diffuse emission.  Modeling the galactic diffuse emission is
very difficult~\ref{first_diffuse_paper}  and finding sources on top of
this emission is notoriously difficult. This issue has been discussed
in the Fermi catalog~\ref{first_cat,2fgl}. Furthermore, the galactic plane
is very crowded and there is a degeneracy between an extended source
and multiple point sources. So it is often difficult to ensure you have
a good model for the region around a source .  Finding a source with
$\tsext>16$ is not sufficient for detecting an extended and we had to
perform many crosschecks to make sure we had a good fit to our region.

@@

% XXXXXXXXXXXXXXXXXXXXXXXXXXX
% Put example of poorly fit region and how it is difficult to know what
% is going on.
Example Bad fit~\ref{example_bad_fit}

@@

Using events above $10\gev$, we were able to succesffuly fit the extesion
of HESS J1825-137\cite{fermi_hess_j1825}. Our analysis of MSH 15-52 using
events above $10\gev$ found an extension consistent with the publisehed
result, but with $\tsext=11.2$.\cite{msh1552}. This
is most likely because the published analysis used events above $6\gev$.

@@

AGN are not expected to be spatially resolvable and therefore
provide a good calibration source to demonstrate the efficacy of our
tool. Nevertheless, it would be very interesting if AGN could be
spatially resolved AGN and there are theories that predict
this\cite{pair_halo_paper}.

Following the Fermi-LAT one year catalog, the Fermi collaboration
published a list of the Fermi catalog sources that had a high probability
association with AGN. The first year catalog had 709 AGN associated with
671 distinct 1FGL sources at high latitude ($|b|>10\deg$).  For our
study, we are looking to assess systematics with extension fitting so
it is important to avoid any possible issues with AGN associations.
For that reason, we select only the 599 AGN which make it into the
``clean'' AGN sample. An AGN association is only considered ``clean''
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the 1FGL source, and if there are no flags
on the source which shed doubt on the source\cite{first_cat}. These last two
conditions are especially important for our analysis. One might expect
source confusion between two AGN look like a spatially extended source.
Testing only unflagged sources is also important because it removes
any catalog sources coincident with structures in the diffuse emission.
It is possible that these flagged catalog sources which are really poorly
modeled diffuse emission might also look extended.

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{This is the Fermi LAT's sensitivity to spatially
    extended sources. The $x$ axis is Monte Carlo extension of a
    simulated uniform disk source and the $y$ axis is the simulated
    source's $100\mev$ to $100\gev$ photon flux. Each curve represents
    the detection threshold for being able to spatially resolve an
    extended source (when $\langle\tsext\rangle=25$ averaged over
    multiple simulations).  
    All sources have an assumed powerlaw spectrum and the different
    colors are for sources of different simulated spectral indices.
    The dashed line shows simulations using events with energy between 
    $100\mev$ and $100\gev$ while the solid lien shows simulations
    using events with energy between $1\gev$ and $100\gev$.
    The sensitivity is for a one year simulation against a Sreekumar-like
    isotropic background (\cite{sreekumar_isotropic}).
    This plot shows that our sensitivity is best for sources that are
    about $1\deg$ large. It also shows that for sources That are neither
    very large nor very soft, our sensitivity is not significantly
    improved using events between $100\mev$ and $1\gev$.  More information
    about this plot is presented in section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{source_plots/example_bad_fit.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v2
    \caption{Example bad Fit: P72Y3047}
    \label{example_bad_fit}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
  \caption{1FGL J1628.6-2419c. In the opiucus region=most likeliy a molecular cloud.
  P72Y2516.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %Note that unlike other plots, that this plot has the nearby sources subtracted.
  %This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
  %which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  }\label{1FGL_J1628.6-2419c}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
  \caption{1FGL J0823.3-4248. P72Y1212. Coincident with Puppis A SNR.
  P72Y1212.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %Note that unlike most other plots, this plot has the nearby sources subtracted.
  %This was done to remove the very bright source Vela which,
  %at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
  %would otherwise spill over into the top left of the image.
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
  }\label{1FGL_J0823.3-4248}
\end{figure}
